DeepAutoTrack (DAT): Vehicle Trajectory Prediction for Autonomous Driving

### 2018-01-19 paper/cvpr2018RebuttalKit/egrebuttal_3790.tex

\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}

% Include other packages here, before hyperref.

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}

%%%%%%%%% PAPER ID  - PLEASE UPDATE
\def\cvprPaperID{3790} % *** Enter the CVPR Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

\begin{document}

%%%%%%%%% TITLE - PLEASE UPDATE
\title{\LaTeX\ Guidelines for Author Response}  % **** Enter the paper title here

\maketitle
\thispagestyle{empty}

%%%%%%%%% BODY TEXT - ENTER YOUR RESPONSE BELOW
\section{Introduction}
The reviewers generally acknowledge the extensibility of our framework, well evaluated experiments, and the novelty of introducing ergodic state to perform segmentation and recognition within the same framework. Due to space constraints, we address only the major criticisms below.

\subsection{R2}

\noindent \textbf{Who else has experimented on the SYNTHIA dataset? Or are the authors the first ones? Are the authors releasing a specific publicly-available prediction challenge based on SYNTHIA?}
Currently, experiments on the SYNTHIA dataset~\cite{HernandezBMVC17,ros2016synthia} focus on single frame, static images for semantic labeling or scene representation. To our knowledge, our paper is the first attempt to utilize continuous video streams for the prediction problems.
are required for the purpose of car trajectory prediction. We
collect car trajectory prediction dataset based on the SYN-
THIA [29] dataset.

Where are comparisons with other activity forecasting/trajectory
prediction works?
I think the authors should reimplement SocialLSTM for 2D data (Stanford
UAV dataset seems to be a 2D standard prediction task -- just throw
away images and just use the xy plane coordinates, e.g. center of
detected bounding box).
SocialLSTM used “Avg. disp. Error”, “Avg. non-linear disp. error” , and
“final disp. Error”
What was the justification for the metrics the authors chose?
In the SocialLSTM paper’s Related Work section, there are about 20
sources that focus on “Activity forecasting”
The details about the fusion of “location” and “semantic” information into
the LSTM hidden state seemed missing (was a bit vague). A figure of the
architecture of the SEG-LSTM would go a long way in clarifying this (or
are the authors using Xu et al.'s "End-to-end Learning of Driving Models
from Large-scale Video Datasets" FCN-LSTM from Trevor Darrell's
group?).
How is this more than just an engineering pipeline, combining tracking
(distilling bounding boxes to coordinates), and then adding an LSTM?
SocialLSTM already did the second part in principle.
I was a bit confused about why the “tracking-by-detection” framework
was novel -- how is it different from “Tracking-learning-detection” (TLD),
from Z. Kalal, K. Mikolajczyk, and J. Matas. In TPAMI 2012?
Why are scene semantics privileged (which you also call “auxiliary”)
information?
If the pipeline relies on fusing the “location” and “semantic” stream, if
privileged information is missing at test time, then won’t the pipeline
break? (privileged information is usually present at train time, but
absent at test time).
Can multiple objects be tracked at once, or just one? The video in the
supplementary material only showed one object being tracked. What was
the average number of objects in each SYNTHIA scene frame?
The focus of the paper seems a bit unclear: apparently, the goal is to
“predict car’s future odometry given previous egomotion visual input”.
But the paper is about prediction of other vehicles’ trajectories, not
about predicting one’s own car odometry (which is different).
Odometry: “Odometry is the use of motion sensors to determine the
robot's change in position relative to some known position” (not other
robots' positions) https://groups.csail.mit.edu/drl/courses/cs54-
2001s/odometry.html
“Visual Odometry -- Estimating the motion of a camera in real time using
sequential images (i.e., egomotion)”
\verb+http://www.cs.toronto.edu/~urtasun/courses/CSC2541/03_odometry.pdf+
(but we are not trying to estimate the motion of a camera-mounted
vehicle here).
I felt like the detection/tracking theme slightly bogs down the main focus
of prediction in the paper. I think refocusing it on prediction would
strengthen the argument.
Line 124 - The authors discuss a "lack of proper metrics for evaluating
the temporal prediction result." How are the current metrics poorly
suited to the task? What would be better?

\subsection{Old}
After receiving paper reviews, authors may optionally submit a rebuttal to address the reviewers' comments, which will be limited to a {\bf one page} PDF file.  Please follow the steps and style guidelines outlined below for submitting your author response.

Note that the author rebuttal is optional and, following similar guidelines to previous CVPR conferences, it is meant to provide you with an opportunity to rebut factual errors or to supply additional information requested by the reviewers. It is NOT intended to add new contributions (theorems, algorithms, experiments) that were not included in the original submission and were not requested by the reviewers. You may optionally add a figure, graph or proof to your rebuttal to better illustrate your answer to the reviewers' comments.

The rebuttal must adhere to the same blind-submission as the original submission and must comply with this rebuttal-formatted template.

%-------------------------------------------------------------------------

Author responses must be no longer than 1 page in length including any references and figures.  Overlength responses will simply not be reviewed.  This includes responses where the margins and formatting are deemed to have been significantly altered from those laid down by this style guide.  Note that this \LaTeX\ guide already sets figure captions and references in a smaller font.

%------------------------------------------------------------------------
\section{Formatting your Response}

{\bf Make sure to update the paper title and paper ID in the appropriate place in the tex file.}

All text must be in a two-column format. The total allowable width of the text
area is $6\frac78$ inches (17.5 cm) wide by $8\frac78$ inches (22.54 cm) high.
Columns are to be $3\frac14$ inches (8.25 cm) wide, with a $\frac{5}{16}$ inch
(0.8 cm) space between them. The top margin should begin
1.0 inch (2.54 cm) from the top edge of the page.  The bottom margin should be
1-1/8 inches (2.86 cm) from the bottom edge of the page for $8.5 \times
11$-inch paper; for A4 paper, approximately 1-5/8 inches (4.13 cm) from the
bottom edge of the page.

Please number all of your sections and any displayed equations.  It is important
for readers to be able to refer to any particular equation.

Wherever Times is specified, Times Roman may also be used.  Main text should be
in 10-point Times, single-spaced. Section headings should be in 10 or 12 point
Times.  All paragraphs should be indented 1 pica (approx. 1/6 inch or 0.422
cm).  Figure and table captions should be 9-point Roman type as in
Figure~\ref{fig:onecol}.

%-------------------------------------------------------------------------
\subsection{References}

List and number all bibliographical references in 9-point Times, single-spaced,
at the end of your response. When referenced in the text, enclose the citation
number in square brackets, for example~\cite{Authors14}.  Where appropriate,
include the name(s) of editors of referenced books.

\begin{figure}[t]
\begin{center}
\fbox{\rule{0pt}{1.8in} \rule{0.9\linewidth}{0pt}}
   %\includegraphics[width=0.8\linewidth]{egfigure.eps}
\end{center}
   \caption{Example of caption.  It is set in Roman so that mathematics
   (always set in Roman: $B \sin A = A \sin B$) may be included without an
   ugly clash.}
\label{fig:long}
\label{fig:onecol}
\end{figure}

%-------------------------------------------------------------------------
\subsection{Illustrations, graphs, and photographs}

All graphics should be centered.  Please ensure that any point you wish to make is resolvable in a printed copy of the response.  Resize fonts in figures to match the font in the body text, and choose line widths which render effectively in print.  Many readers (and reviewers), even of an electronic copy, will choose to print your response in order to read it.  You cannot insist that they do otherwise, and therefore must not assume that they can zoom in to see tiny details on a graphic.

When placing figures in \LaTeX, it's almost always best to use \verb+\includegraphics+, and to specify the  figure width as a multiple of the line width as in the example below
{\small\begin{verbatim}
   \usepackage[dvips]{graphicx} ...
   \includegraphics[width=0.8\linewidth]
                   {myfile.eps}
\end{verbatim}
}

{\small
\bibliographystyle{ieee}
\bibliography{egbib}
}

\end{document}

### 2018-01-19 paper/cvpr2018/cvpr2018_3790.tex
rebuttal template added

\def\cvprPaperID{16} % *** Enter the CVPR Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}
\begin{document}

@@

Vision-based deep neural networks are crucial components for autonomous driving in terms of visual understanding and decision making.
These models need to be temporally consistent and visually interpretable.
Most recent works focus on using static images for understanding visual semantics, ignoring the temporal consistency of driving conditions; or adopt end-to-end architectures for learning the pilot networks, providing limited interpretability.
In this paper, we raise the question of ``can we predict car's future odometry given previous egomotion visual input?".
The proposed system stems from the issue of human driver reaction time in the autonomous driving context.
Our dual-staged model firstly applies modern convolutional object detectors for spotting traffic participants (i.e., cars in this paper) and robustly tracks the targets of interest.
Then, a novel SEG-LSTM network is incorporated to fuse the multiple-streams from past frames and then predict targets' future trajectories.
We demonstrate the feasibility of predicting future trajectories of vehicles for assisting mediated perception.
 We also show the effectiveness of using privileged information (e.g., scene semantics) further boost the prediction accuracy across diverse traffic conditions.
\end{abstract}
%%%%%%%%% BODY TEXT
%%% Andrje Karpathy's blog: http://karpathy.github.io/2016/09/07/phd/
%%% Another great resource on this topic is Tips for Writing Technical Papers from Jennifer Widom.
%%% https://cs.stanford.edu/people/widom/paper-writing.html
\section{Introduction}

%\textbf{\emph{1.1 What is the problem?}}

Currently, there are two major paradigms for autonomous driving systems built upon vision-based input~\cite{chen2015deepdriving}: mediated perception approaches that firstly explain the vision input and then parse the scene to make a driving policy (usually by a controller with if-then-else rules); and behaviour reflex approaches that directly map the vision input to a driving policy by a regressor.
In this paper, in the framework of first paradigm, we try to tackle the problem of predicting future trajectories of vehicles given its past information.

@@

\begin{figure}[t]
        \centering
        \includegraphics[width=0.45\textwidth]{figures/pull_figure.pdf}
        \caption{ {\small We propose a system to predict future trajectories of vehicles. Given a historical information, obtained by detection, tracking and semantic segmentation, a network based on Long Short Term Memory (LSTM) structure is trained to generate future information.}}
        \label{fig:pull_figure}
\end{figure}

%\textbf{\emph{1.4. Why hasn't it been solved before? (Or, what's wrong with previous proposed solutions? How does mine differ?)}}
Vehicles trajectory prediction is also very related to visual tracking.
In traditional vision based tracking problems (\emph{e.g.},~\cite{wu2013online, wu2015object, mueller2016benchmark}) where target objects go through rather sporadic movements (usually the object trajectory is generated by artificial movement in order to test the robustness of the tracker), the prediction of target's future trajectory is simply a moot problem.
However, traffic participants generally exhibit regular trajectories (\emph{e.g.,} cars driving on the road, pedestrians walking on the sidewalks). Given law-abiding traffic participants, human drivers subconsciously project visual target's future trajectory.
Nonetheless, due to the missing bridge between traditional visual tracking community and current autonomous driving research community, there is a lack of proper metrics for evaluating the temporal prediction result.

@@

%\textbf{\emph{1. Object detection, segmentation, instance segmentation}}
%\subsection{Traffic participants detection and tracking: object detection and instance association}
\subsection{Object detection}
Vehicle detection is one key component of an autonomous driving system. Typical algorithms output bounding boxes on detected vehicles.
A lot of progess has been made in recent years on object detection due to the use of convolutional neural networks (CNNs).
Modern object detectors based on these networks -- such as the line of works on the R-CNN~\cite{girshick2014rich},
Fast R-CNN~\cite{Girshick2015Fast}, Faster R-CNN~\cite{ren2015faster_nips}, Mask R-CNN~\cite{he2017mask} and  SSD~\cite{liu2016ssd} -- are now good enough to be deployed in a consumer products.
% Before the resurgence of convolutional neural network (CNN), Deformable Part Model (DPM) \cite{felzenszwalb2008discriminatively} and Selective Search \cite{Uijlings2013Selective} are the trend of this field.
% However, after the proposal of
 R-CNN~\cite{girshick2014rich} combines Selective Search and deep learning features to detect objects.
 % At the beginning, R-CNN is a step-by-step and inefficient method. Then,
  SPPNet \cite{He2015Spatial} exploits a spatial pyramid pooling layer to extract multi-scale deep features. Later Fast R-CNN~\cite{Girshick2015Fast} introduces the multi-task learning to fine-tune all layers in their network. At last, Faster R-CNN \cite{ren2015faster_nips} proposes a region proposal network (RPN) and integrates RPN and Fast R-CNN to build a end-to-end architecture. Meanwhile, SSD \cite{liu2016ssd} uses a series of boxes and directly gives the probability for each object class. In addition, YOLO \cite{redmon2016you} proposes a fast object detection method, which divides the input image into grids, then predicts object positions and confidences for each category in each grid.

@@

\begin{figure*}[t]
        \centering
        \includegraphics[width=0.95\textwidth]{figures/framework.pdf}
        \caption{ {\small The framework of our vehicle future trajectory prediction system. The input is the sequence data from a synthetic scene in \cite{mueller2016benchmark}. Historical information are extracted by detection & tracking and semantic segmentation. All of the information is fed into our LSTM model to predict future trajectories.}}
        \label{fig:framework}
\end{figure*}

@@

Vision-based semantic segmentation in urban scene is a key functionality for autonomous driving.
%Camvid dataset~\cite{Camvid} consists of a set of monocular images taken in Cambridge UK. However, only 701 images contain pixel-level annotations over a total of 32 categories (combining objects and architectural scenes).
%Similarly, Daimler Urban Segmentation dataset~\cite{scharwachter2013efficient} contains 500 fully labelled monochrome frames for 5 categories.
KITTI benchmark suite~\cite{Geiger2013IJRR} provides a large a mount of images of urban scene from Karlsruhe, Germany, with ground truth data for odometry, object detection, tracking, scene flow and stereo benchmarks. However, a limited 430 labelled images are provided for semantic segmentation.
%A common limitation of the aforementioned datasets is the bias introduced by the acquisition of images in a specific city. The LabelMe~\cite{russell2008labelme} project offers the solution by offering around 1,000 fully annotated images of urban environments around the world and more than 3,000 images with partial(noisy) annotations.
More recently, larger project are constructed:
Cityscapes dataset~\cite{Cordts2016Cityscapes} which consists of a collection of images acquired in 50 cities around Germany, Switzerland and France in difference seasons, and having 5,000 images with fine annotations and 20,000 with coarse annotations over a total of 30 classes. Comma.ai~\cite{santana2016learning} provides 7 and a quarter hours of largely highway driving. Udacity~\cite{udacity} dataset includes 65,000 labels across 9,423 frames at full resolution of $1920\times1200$ at 2Hz.
The use of synthetic data has increased considerably in recent years within computer vision community. A synthetic dataset named Synthia is\cite{mueller2016benchmark} provide originally for urban scene semantic segmentation generation.
%In~\cite{kaneva2011evaluation}, the authors used a photorealistic virtual world to evaluate the performance of image features under scene changes and image transformations. Synthetic data has also been used for skeleton joints estimation~\cite{shotton2013real}, allowing the classifier invariant to pose, body shape, clothing, etc.
Synthetic dataset has an obvious advantage: a fine annotated images in Cityscape dataset requires on average 1.5 hours which is very labor intensive. Thus, the cost of scaling large project would required a prohibitive economic investment in order to capture images from a larger variety of countries, in different seasons and different traffic conditions.
%For these reasons, a novel synthetic dataset of urban scene called SYNTHIA~\cite{ros2016synthia} is proposed to use synthetic imagery that simulate real urban scenes in a vast variety of conditions and produce the appropriate annotations.
%This dataset is a large collection of images with high variability due to changes in illumination, textures, pose of dynamic objects and camera view-points.

@@

We first describe our overall approach for vehicle trajectory prediction and the details of implementation are presented in Sec~\ref{sec:Implementations}.
Our goal is via collecting the visual information from the past to predict the traffic participants future trajectory. Fig.~\ref{fig:framework} shows the overall architecture of our proposed framework.

\subsection{Generic 3D Traffic Participants Trajectory Prediction}

We propose to learn a generic approach from history information and formulate the problem as predicting future traffic participants' trajectories.
Our work is most related to~\cite{xu2017end} where the problem was to predict future feasible actions of egomotion from a motion reflex perspective.
We, instead,  predict other traffic participants' future trajectories.
Formally, our problem can be defined as a mapping between historical trajectory $ \{h_t^p\}, t=1,\dots, T $ with auxiliary information $ \{a_t^p\}, t=1,\dots, T $ for traffic participant $p$ and the future trajectory $\{j_t^p\}, t={T+1}, \ldots$:

\begin{equation}
\bm{\mathcal{M}}_p(h, a): H \times A  \rightarrow J
\label{eq:mapping}
\end{equation}
where the traffic participants $p$ can be of vehicles, cyclists, pedestrians, \emph{etc}. Historical and future trajectories are defined in a 3D occupancy grid:
\begin{equation}
H, J \in \Re^{6} =  \{x, y, w, h, d_{min}, d_{max}\}
\label{eq:mapping2}
\end{equation}
where $\{x,y,w,h\}$ define target's 2D boundingbox in image pixel space and $\{d_{min}, d_{max}\}$ define the minimum and maximum relative distance between host car and the tracking target acquired from the depth camera. Given RGB cameras' focal length $f$, the pixel space 2D boundingbox can be projected into 3D real-world coordinate $\{x_r,y_r,w_r,h_r\}$ as:
\begin{align}
    x_r = \frac{x}{f}d &, y_r = \frac{y}{f} d  \label{eq:focal_length_1}  \\
    w_r = \frac{w}{f}d &, h_r = \frac{h}{f} d
    \label{eq:focal_length_2}
\end{align}
where $d$ is distance between  the center of the lens and the center of target and we use $d_{min}$ as a close approximation.

@@

\begin{figure}[t]
        \centering
        \includegraphics[width=0.5\textwidth]{figures/network_detail.pdf}
        \caption{ {\small Different networks to predict future trajectory. Left: FrameToFrame, using historical trajectories with many-to-many LSTM to predict; Middle:FrameToSeq, using historical trajectories with many-to-many LSTM ; Right:SEG-LSTM, the proposed model by using historical trajectories and semantic segmentation information.}}
        \label{fig:dataset}
\end{figure}
\subsection{SEG-LSTM Architecture}

We compare two temporal models based on LSTM cells for predicting the car trajectory.
Results show that the temporal model generating intermediate output utilizing the whole historical data performs better than the frame-to-frame based output temporal model.

As shown in figure 3, we compare three temporal models based on LSTM cells for predicting the car trajectory. The first architecture(FtoF) is akin to a language model, which predicts the next occupancy grid frame-to-frame.  At test-time, it samples current predicted 3D occupancy as feedback to the model for predicting next occupancy. At time-step t, the architecture utilizes all past historical trajectory up to time-step t  to predict 3D occupancy of the tracking car in next frame. This architecture uses a 3-hidden-layer LSTM model followed by a fully connected network at last LSTM hidden layer each time-step. The LSTM model has 100, 300, 300 hidden states in each layer respectively, and the fully connected network concludes one hidden layer followed by a ReLU activation layer.

The second architecture(FtoS) is also composed of LSTM part and fully connected part, which are same as the one of the FtoF architecture, but the connecting method is different. Rather than predicting frame-to-frame, this architecture can directly predict a trajectory sequences. FtoS uses an LSTM as an encoder to fuse all past trajectory information into a single LSTM hidden state, corresponding to the hidden state in last LSTM layer at last time-step T. This state is complete, in the sense it contains all historical trajectory information of the tracking car. And then we use a fully connected network as decoder to directly predict trajectory during next continuous frames.

In addition to  historical trajectory information, the third architecture(SEG-LSTM) also fuses semantics of  historical frames as auxiliary information. The input to the bottom-most LSTM layer is the 3D occupancy of historical trajectory. The second LSTM layer fuses the outputs of the bottom-most LSTM with the frame's semantic information, which is extracted from the semantic segmentation through a four-layer CNN, to produce a joint representation of the semantic auxiliary information and the historical trajectory.  As described above, the 3D occupancy just has six dimensions,{x, y, w, h, dmin, dmax}. So the bottom-most LSTM not only can learn the temporal information between time-varing trajectory,  but also can balance trajectory information and the semantic information. The LSTM part  and fully connected part is same as the one of above two architecture, and the CNN part is composed of four convolutional block. Each block includes a convolutional layer, a ReLU activation layer, a Maxpooling layer and a dropout layer except for the last block which has no dropout layer. Each convolutional layer has four channels and 3¡Á3 kernel. Results show that the SEG-LSTM model performs better than the other two temporal model.

%\subsection{focal lenes back projection into real world grid}

@@

\subsection{Dataset collection}

>>>>

\def\cvprPaperID{3790} % *** Enter the CVPR Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}
\begin{document}

@@

Vision-based deep neural networks are crucial components for autonomous driving in terms of visual understanding and decision making.
These models need to be temporally consistent and visually interpretable.
Most recent works focus on using static images for understanding visual semantics, ignoring the temporal consistency of driving conditions; or adopt end-to-end architectures for learning the pilot networks, providing limited interpretability.
In this paper, we raise the question of ``can we predict car's future odometry given previous egomotion visual input?".
The proposed system stems from the issue of human driver reaction time in the autonomous driving context.
Our dual-staged model firstly applies modern convolutional object detectors for spotting traffic participants (i.e., cars in this paper) and robustly tracks the targets of interest.
Then, a novel SEG-LSTM network is incorporated to fuse the multiple-streams from past frames and then predict targets' future trajectories.
We demonstrate the feasibility of predicting future trajectories of vehicles for assisting mediated perception.
 We also show the effectiveness of using privileged information (e.g., scene semantics) further boost the prediction accuracy across diverse traffic conditions.
\end{abstract}
%%%%%%%%% BODY TEXT
%%% Andrje Karpathy's blog: http://karpathy.github.io/2016/09/07/phd/
%%% Another great resource on this topic is Tips for Writing Technical Papers from Jennifer Widom.
%%% https://cs.stanford.edu/people/widom/paper-writing.html
\section{Introduction}
\begin{figure}[t]
        \centering
        \includegraphics[width=0.45\textwidth]{figures/pull_figure.pdf}
        \caption{ {
        We propose a system to predict future trajectories of vehicles. Given historical information, obtained by detection, tracking and semantic segmentation, a multi-stream Long Short Term Memory (LSTM)  based network is trained to generate future trajectory.}}
        \label{fig:pull_figure}
\end{figure}
%\textbf{\emph{1.1 What is the problem?}}

Currently, there are two major paradigms for autonomous driving systems built upon vision-based input~\cite{chen2015deepdriving}: mediated perception approaches that firstly explain the vision input and then parse the scene to make a driving policy (usually by a controller with if-then-else rules); and behaviour reflex approaches that directly map the vision input to a driving policy by a regressor.
In this paper, in the framework of first paradigm, we try to tackle the problem of predicting future trajectories of vehicle given its past information.

@@

%\textbf{\emph{1.4. Why hasn't it been solved before? (Or, what's wrong with previous proposed solutions? How does mine differ?)}}
Vehicle trajectory prediction is also very related to visual tracking.
In traditional vision based tracking problems (\emph{e.g.},~\cite{wu2013online, wu2015object, mueller2016benchmark}) where target objects go through rather sporadic movements (usually the object trajectory is generated by artificial movement in order to test the robustness of the tracker), the prediction of target's future trajectory is simply a moot problem.
However, traffic participants generally exhibit regular trajectories (\emph{e.g.,} cars driving on the road, pedestrians walking on the sidewalks). Given law-abiding traffic participants, human drivers subconsciously project visual target's future trajectory.
Nonetheless, due to the missing bridge between traditional visual tracking community and current autonomous driving research community, there is a lack of proper metrics for evaluating the temporal prediction result.

@@

%\textbf{\emph{1. Object detection, segmentation, instance segmentation}}
%\subsection{Traffic participants detection and tracking: object detection and instance association}
\subsection{Object detection}
Vehicle detection is one key component of an autonomous driving system. Typical algorithms output bounding boxes on detected vehicles.
A lot of progess has been made in recent years on object detection due to the use of convolutional neural networks (CNNs).
Modern object detectors based on these networks -- such as the line of works on the R-CNN~\cite{girshick2014rich},
Fast R-CNN~\cite{Girshick2015Fast}, Faster R-CNN~\cite{ren2015faster_nips}, Mask R-CNN~\cite{he2017mask} and  SSD~\cite{liu2016ssd} -- are now good enough to be deployed in a consumer products.
% Before the resurgence of convolutional neural network (CNN), Deformable Part Model (DPM) \cite{felzenszwalb2008discriminatively} and Selective Search \cite{Uijlings2013Selective} are the trend of this field.
% However, after the proposal of
 R-CNN~\cite{girshick2014rich} combines Selective Search and deep learning features to detect objects.
 % At the beginning, R-CNN is a step-by-step and inefficient method. Then,
  SPPNet \cite{He2015Spatial} exploits a spatial pyramid pooling layer to extract multi-scale deep features. Later Fast R-CNN~\cite{Girshick2015Fast} introduces the multi-task learning to fine-tune all layers in their network. At last, Faster R-CNN \cite{ren2015faster_nips} proposes a region proposal network (RPN) and integrates RPN and Fast R-CNN to build an end-to-end architecture. Meanwhile, SSD \cite{liu2016ssd} uses a series of boxes and directly gives the probability for each object class. In addition, YOLO \cite{redmon2016you} proposes a fast object detection method, which divides the input image into grids, then predicts object positions and confidences for each category in each grid.

@@

\begin{figure*}[t]
        \centering
        \includegraphics[width=0.95\textwidth]{figures/framework.pdf}
        \caption{
        The framework for the proposed vehicle future trajectory prediction system. The input is the sequential data obtained from the host car. Historical information is extracted by detection \& tracking. Along with scene semantics as an auxiliary information, multi-stream inputs are fed into our LSTM model to predict future trajectories.}

        \label{fig:framework}
\end{figure*}

@@

Vision-based semantic segmentation in urban scene is a key functionality for autonomous driving.
%Camvid dataset~\cite{Camvid} consists of a set of monocular images taken in Cambridge UK. However, only 701 images contain pixel-level annotations over a total of 32 categories (combining objects and architectural scenes).
%Similarly, Daimler Urban Segmentation dataset~\cite{scharwachter2013efficient} contains 500 fully labelled monochrome frames for 5 categories.
KITTI benchmark suite~\cite{Geiger2013IJRR} provides a large a mount of images of urban scene from Karlsruhe, Germany, with ground truth data for odometry, object detection, tracking, scene flow and stereo benchmarks. However, a limited 430 labelled images are provided for semantic segmentation.
%A common limitation of the aforementioned datasets is the bias introduced by the acquisition of images in a specific city. The LabelMe~\cite{russell2008labelme} project offers the solution by offering around 1,000 fully annotated images of urban environments around the world and more than 3,000 images with partial(noisy) annotations.
More recently, larger projects are constructed:
Cityscapes dataset~\cite{Cordts2016Cityscapes} which consists of a collection of images acquired in 50 cities around Germany, Switzerland and France in difference seasons, and having 5,000 images with fine annotations and 20,000 with coarse annotations over a total of 30 classes. Comma.ai~\cite{santana2016learning} provides 7 and a quarter hours of largely highway driving. Udacity~\cite{udacity} dataset includes 65,000 labels across 9,423 frames at full resolution of $1920\times1200$ at 2Hz.
The use of synthetic data has increased considerably in recent years within computer vision community. A synthetic dataset named SYNTHIA~\cite{mueller2016benchmark} is originally provided for urban scene semantic segmentation generation.
%In~\cite{kaneva2011evaluation}, the authors used a photorealistic virtual world to evaluate the performance of image features under scene changes and image transformations. Synthetic data has also been used for skeleton joints estimation~\cite{shotton2013real}, allowing the classifier invariant to pose, body shape, clothing, etc.
Synthetic dataset has an obvious advantage: a fine annotated image in Cityscape dataset requires on average 1.5 hours which is very labor intensive. Thus, the cost of scaling large project would require a prohibitive economic investment in order to capture images from a larger variety of countries, in different seasons and different traffic conditions.
%For these reasons, a novel synthetic dataset of urban scene called SYNTHIA~\cite{ros2016synthia} is proposed to use synthetic imagery that simulate real urban scenes in a vast variety of conditions and produce the appropriate annotations.
%This dataset is a large collection of images with high variability due to changes in illumination, textures, pose of dynamic objects and camera view-points.

@@

We first describe the overall framework for vehicle trajectory prediction and the details of implementation are presented in Sec~\ref{sec:Implementations}.
Our goal is via collecting visual information from the past frames to predict the traffic participants future trajectory. Fig.~\ref{fig:framework} shows the overall architecture of the proposed framework.

\subsection{3D Traffic Participants Trajectory Prediction}

We propose to learn a generic approach from history information and formulate the problem as predicting future traffic participants' trajectories.
Our work is most related to~\cite{xu2017end} where the problem was to predict future (next 1/3rd second) feasible actions of egomotion from a motion reflex perspective.
We, instead,  predict other traffic participants' future trajectories in a longer time span (next 1.6 second).
Formally, our problem can be defined as a mapping $\mathcal{M}$ between historical trajectory $H=\{h_t^p\}, t=1,\dots, T $ with auxiliary information $ A=\{a_t^p\}, t=1,\dots, T $ for traffic participant $p$ and the future trajectory $J=\{j_t^p\}, t={T+1}, \ldots$:

\begin{equation}
J \leftarrow \bm{\mathcal{M}}_p(h, a): H \times A
\label{eq:mapping}
\end{equation}
where the traffic participants $p$ can be of vehicles, cyclists, pedestrians, \emph{etc}. In this paper, we focus on vehicle as the sole traffic participant category and ignore the suffix $p$ from now on. Historical and future trajectories are defined in a 3D occupancy grid:
\begin{equation}
H, J \in \Re^{6} =  \{x, y, w, h, d_{min}, d_{max}\}
\label{eq:mapping2}
\end{equation}
where $\{x,y,w,h\}$ define target's 2D boundingbox in image pixel space and $\{d_{min}, d_{max}\}$ define the minimum and maximum relative distance between host car and the tracking target (acquired from the depth camera). Given RGB cameras' focal length $f$, the pixel space 2D boundingbox can be projected into 3D real-world coordinates $\{x_r,y_r,w_r,h_r\}$ as:
\begin{align}
    x_r = \frac{x}{f}d &, y_r = \frac{y}{f} d  \label{eq:focal_length_1}  \\
    w_r = \frac{w}{f}d &, h_r = \frac{h}{f} d
    \label{eq:focal_length_2}
\end{align}
where $d$ is distance between  the center of the camera lens and the center of target. We use the minimum relative distance $d_{min}$ is as a close approximation.

@@

\begin{figure}[t]
        \centering
        \includegraphics[width=0.52\textwidth]{figures/network_detail.pdf}
        \caption{Illustrations of three temporal networks. $H$ represents historical trajectories, $J$ is the $T$ time step trajectories to be predicted.  Left: Frame-to-Frame (FtF); Middle:Frame-to-Sequence (FtS); Right:SEG-LSTM, with extra auxiliary information as input $A$.}
        \label{fig:lstm}
\end{figure}

\subsection{Sequence modeling}

For predicting vehicle's future trajectory, we compare three temporal models based on LSTM cells  as shown in Fig.~\ref{fig:lstm}. The first two models take sequential 3D occupancy as input. In the third model, we  explore using semantic segmentation as a side ``auxiliary" information to better guide the trajectory prediction.

\vspace{\baselineskip}
\noindent \textbf{Frame-to-Frame (FtF) model:}
is akin to character prediction in a language model.  At test-time $t$, it samples current predicted 3D occupancy as feedback to the model for predicting next frame occupancy grid. The model is frame to frame Markovian and the next frame trajectory $j_t$ can be estimated as:
\begin{equation}
j_t \leftarrow  \bm{\mathcal{M}}_p(j_{t-1}, h): H
\label{eq:FtF}
\end{equation}

\vspace{\baselineskip}
\noindent \textbf{Frame-to-Sequence (FtS) model:}
differs from the FtF model in that instead of sampling frame by frame for predicting future trajectories,   FtS model directly predicts a trajectory sequence of length $T$ (corresponding to the total driver reaction time). The assumption is that current state is complete, in the sense it contains all historical information required for predicting the future trajectory of the vehicle. The whole trajectory  $j_{t, t+1, \ldots, T}$ to be predicted can be estimated as:
\begin{equation}
j_{t, t+1, \ldots, T}, \leftarrow  \bm{\mathcal{M}}_p( h): H
\label{eq:FtS}
\end{equation}

\vspace{\baselineskip}
\noindent \textbf{SEG-LSTM model:}
 take advantages of scene semantics from  historical frames as auxiliary information $A$. The second LSTM layer fuses the outputs from the bottom-most LSTM with the current frames's higher level semantic information. Semantic inputs are one-hot encoded images with channel number $C$ as the number of semantic category. The higher level semantic is extracted from the semantic input through a four-layer CNN, producing a joint representation of the semantic auxiliary information and the historical trajectory.  As described above, the 3D occupancy just has six dimensions: $[x, y, w, h, d_{min}, d_{max}]$. So the bottom-most LSTM not only can learn the temporal information between time-varing trajectory,  but also can balance input dimensions of both trajectory information and the semantic information.
%Results show that the SEG-LSTM model performs better than the other two temporal model.
Note that this model differs from that of~\cite{xu2017end} in that instead of using semantic segmentation as a side task for better directing the learning process of the convnets, SEG-LSTM directly takes scene semantics as input and directs the recurrent net future trajectory prediction. With auxiliary $A$, the trajectory  $j_{t, t+1, \ldots, T}$  to be predicted can be estimated as:

\begin{equation}
j_{t, t+1, \ldots, T}, \leftarrow  \bm{\mathcal{M}}_p(h, a): H \times A
\label{eq:SEG-LSTM}
\end{equation}

@@

We first provide the data collection procedure for vehicle trajectory prediction. And then we present the implementation details with performance analysis of individual modules. Quantitatively examination of SEG-LSTM architecture is also presented showing the advantages of using semantics directly as input can better assist the neural net's trajectory prediction.

\subsection{Dataset collection}
\begin{algorithm}[h]
\begin{algorithmic}
\caption{\textbf{Car trajectory ground truth collection}}\label{list:dataset_collection}
\STATE \textbf{Step 1} $\rightarrow $ acquiring traffic participants from ground truth annotations with only ``car" as instances.
\STATE \textbf{Step 2} {$\rightarrow $ acquiring frame-based instance information:
{
\bindent
  \IF{POR $> 0.2\%$}
    %\bindent[1.45cm]
    \STATE $\Rightarrow$ start tracking instance;
    \STATE $\Rightarrow$ collecting 3D tracking boundingbox: $[x, y, w, h, d_{min}, d_{max}]$;
    \STATE $\Rightarrow$ collecting semantic labeling image $I_{seg}$;
    \STATE $\Rightarrow$ collecting 2D car pose from RGB input $I_{car}$;
    %\eindent
  \ELSIF{POR $< 0.1\%$}
    \STATE $\Rightarrow$ stop tracking.
    \ENDIF\eindent}
  }
\STATE \textbf{Step 3} $\rightarrow $ splitting sequences into tracklets of 23 frames with step size 1:
{\bindent
    \STATE $\Rightarrow$  first 15 frames (5Hz, 3 sec) as training input;
  \STATE $\Rightarrow$  next 8 frames (1.6 sec) as the held-up future trajectory to be predicted.
  \eindent}

\end{algorithmic}
\end{algorithm}
